INGRID: Creating Languages in MPS from ANTLR Grammars

### 2016-10-31 chapters/background.tex
reverting delete of large part of background text

An MPS language is created by the PE4MPS tool in two steps.
First, the PE parser is used to load an input PE file and build its intermediate representation, which has the form of a tree-like structure consisting of Java objects.
Then, all the concepts (AST nodes) and their aspects are created inside MPS.
The information about the code layout, extracted from the PE file, is used when generating the projectional editor for every AST node.

The main disadvantage of the PE4MPS approach is that it only shifts the tedious manual work from creating projectional editors in the MPS IDE to writing PE grammars in plain text.
Usage of a standard text editor is inferior (and much more error-prone) with respect to MPS, which has been designed for the purpose of specifying the code layout and provides lot of support to developers.
Another limitation of PE4MPS is that it does not implement the full ANTLR syntax.
Every grammar might require non-trivial adjustments before it can be processed using the PE4MPS tool.
To compare, the goals behind our INGRID approach are (1) to enable import of as many languages as possible out-of-the-box with maximal automation and (2) to adopt the full specification of every imported language.

>>>>

\PV{Nasledujici dve vety byly vzaty z popisu INGRID, tak funguje INGRID, ne PE4MPS.}
An MPS language is created by the PE4MPS tool in two steps.
First, the PE parser is used to load an input PE file and build its intermediate representation, which has the form of a tree-like structure consisting of Java objects.
Then, all the concepts (AST nodes) and their aspects are created inside MPS.
The information about the code layout, extracted from the PE file, is used when generating the projectional editor for every AST node.

The main disadvantage of the PE4MPS approach is that it only shifts the tedious manual work from creating projectional editors in the MPS IDE to writing PE grammars in plain text.
\PV{Navrhuji pridat (aby to bylo vice jasne?): User is forced to input the layout information by extending the grammar manually.}
Usage of a standard text editor is inferior (and much more error-prone) with respect to MPS, which has been designed for the purpose of specifying the code layout and provides lot of support to developers.
Another limitation of PE4MPS is that it does not implement the full ANTLR syntax.
Every grammar might require non-trivial adjustments before it can be processed using the PE4MPS tool.
To compare, the goals behind our INGRID approach are (1) to enable import of as many languages as possible out-of-the-box with maximal automation and (2) to adopt the full specification of every imported language.
